---
name: Jorge King
surname:  .
position: "Actuarial and Data Science Manager"
address: "Urb. Villa Fontana lote 15B via arrayenes Puembo - Ecuador"
phone: +593 984057673
profilepic: cv.jpg
email: "jkm88877@hotmail.com"
github: jorge.king
linkedin: Jorge-King-M
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "CSPA, Data scientist, actuary, expert in finance, risk managent, predictive analysis, analytics, and data analysis"
output: vitae::twentyseconds
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

 * Knowledge and expierencia in diferrent programing languages: Python, R, SAS, VBA, SQL, Simul8, Vensim, Xpress, STATA, git, docker, APIs
 * Knowledge and expierencia in diferrent data visualization software: Power BI, Tableu, Qlik, Oracle Data Visualization, Power point.
  * Knowledge and expierencia in diferrent finance software: Adaptive planing, Moodys, Excel.
 * I was the first person of my country to gain the CSPA certification of the Casuality Actuarial Society.
  * Maximiun honors in my master degree in UK and scholar of my country to study there.
  
# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Diploma in Actuarial Science", "2018", "Universidad Catolica de Chile", "Santiago - Chile",
  "MSc (Hons) in Operational reseach, applied statistics and risk managment", "2016", "Cardiff University", "Cardiff - United Kingdom",
  "MSc in Corporative Finance", "2015", "Escuela Politecnica del Ejercito ESPE", "Quito - Ecuador",
  "Diploma in Finance Strategy", "2014", "Universidad de la Plata", "La Plata - Argentina",
   "MSc in Finance and Insurence Laws", "2012", "Universidad Andina Simon Bolivar", "Quito - Ecuador",
  "BSc in Marketing", "2012", "Universidad San Francisco de Quito", "Quito - Ecuador",
  "BSc in Bussiness Administration","2012", "Universidad San Francisco de Quito", "Quito - Ecuador",
  "BSc in Laws", "2011", "Universidad de las Americas", "Quito - Ecuador"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Experience
```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Actuarial and data analytics manager", "Quito - Ecuador", "Aseguradora del Sur", "2016 - Actual", "Pricing, reservas, underwriting guide, investment",
  "Actuarial and data analytics manager", "Quito - Ecuador", "Aseguradora del Sur", "2016 - Actual", "Risk managment include financial risk and operational risk",
  "Actuarial and data analytics manager", "Quito - Ecuador","Aseguradora del Sur", "2016 - Actual", "Budget and forecasting",
  "Actuarial and data analytics manager", "Quito - Ecuador", "Aseguradora del Sur",  "2016 - Actual", "Analytics",
  "Actuarial and data analytics manager", "Quito - Ecuador", "Aseguradora del Sur",  "2016 - Actual", "Predictive analysis, scoring, cross and up selling",
  "Actuarial and data analytics manager", "Quito - Ecuador", "Aseguradora del Sur",  "2016 - Actual", "New products",
  "Actuarial and data analytics manager", "Quito - Ecuador", "Aseguradora del Sur",  "2016 - Actual", "Data mining",
    "Research Internship", "United Kingdom", "Lloyds Bank",  "2016", "Control de process of reserves",
    "Research Internship", "United Kingdom", "Lloyds Bank",  "2016", "Behavior and credit risk scoring",
  "Risk and statican analyst", "Quito - Ecuador", "Aseguradora del Sur",  "2014 - 2015", "Forecasting",
    "Risk and statican analyst", "Quito - Ecuador", "Aseguradora del Sur",  "2014 - 2015", "Credit, Liquidity and mercado risk",
    "Risk and statican analyst", "Quito - Ecuador", "Aseguradora del Sur",  "2014 - 2015", "Apetito de riesgo y limites",
    "Risk and statican analyst", "Quito - Ecuador", "Aseguradora del Sur",  "2014 - 2015", "Financial analysis",
    "Risk and statican analyst", "Quito - Ecuador", "Aseguradora del Sur",  "2014 - 2015", "Bussiness Intelligence",
    "Credit risk analyst", "Quito - Ecuador", "Banco Pichincha",  "2010 - 2014", "Economic analysis",
  "Credit risk analyst", "Quito - Ecuador", "Banco Pichincha",  "2010 - 2014", "Risk analysis",
  "Credit risk analyst", "Quito - Ecuador", "Banco Pichincha",  "2010 - 2014", "Financial analysis of finance reports",
  "Credit risk analyst", "Quito - Ecuador", "Banco Pichincha",  "2010 - 2014", "Projects fsactibility",
  "Credit risk analyst", "Quito - Ecuador", "Banco Pichincha",  "2010 - 2014", "forecasting",
  "Credit risk analyst", "Quito - Ecuador", "Banco Pichincha",  "2010 - 2014", "provision of cartera",
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

```{r}
scholar::get_publications("EmD_lTEAAAAJ&EmD_lTEAAAAJ&") %>% 
  filter(cites > 30) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = row_number()) %>% 
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("curie.bib")

bibliography_entries("curie.bib")
```

